Comparing and contrasting with prior work in the field

### 2014-02-20 response/response.tex

\item 
      In other words, how the solutions compare in terms of accuracy and speed between the methods when
      solving given problems? Please include two examples of interest. The authors
      suggest that two examples involving non-linear systems are already included in the
      paper repository.

{\color{red}
  \begin{itemize}
    \item 
        The added section 'Working examples of CS, AD and FD for Newton's method' includes
        the two examples alluded to in the manuscript and requested by the reviewer. 
        % 
        To summarize, in this section is an example of interest: a displacement accuracy study and 
        a convergence rate study on a non-linear beam problem, where each of the methods
        discussed in the manuscript are used individually to solve the problem. 
 \end{itemize}}

\item
      The authors say in the Conclusion: “While the results showed that CS
      produced more accurate tangent-stiffness matrices than CD and FD under
      the parameters of the tests, it was not determined whether or not this is
      a clear advantage of CS over FD in terms of accuracy of final predicted
      displacements and speed of convergence.” This needs to be studied and
      results in this regard added to this manuscript.

{\color{red}
  \begin{itemize}
    \item 
      The added subsection 'Convergence and displacement accuracy studies'
      includes convergence rate and displacement accuracy studies similar to
      those shown in 'Working examples ...', but with the models and tools of
      the main study. This subsection provides an example of interest. 
  \item 
      To summarize, these studies are done in \emph{Peridigm} using the most refined mesh
      from the 'serial' test runs from the original manuscript. Measured was the performance of the methods in terms of speed
      (convergence rate) and accuracy (displacement accuracy).  Iteration speed
      was reported in the original manuscript.
  \item
      It was determined that the accuracy of CS over FD resulted in no appreciable
      advantage in terms of displacement accuracy or convergence rate for the problems
      solved in this study. 
    \item
      Additional comment on the significance of the accuracy of the Jacobian
      to Newton's method is included in the subsections 'For further studies of
      Jacobian accuracy in Newton's method', 'Grain of salt for speed results'
      and 'Remarks'. 
  \item 
      To summarize, Newton's method is insensitive to the accuracy differences
      shown by the methods, for the problems shown, when the methods are not
      deliberately misused with inappropriate step sizes. For completeness,
      formulas describing a relationship between Jacobian accuracy and
      convergence rate order are included. 
  \item
      It is the authors' opinion that the above revisions offer the discussion of relative problem solving
      performance of the methods that the reviewer has requested, including consideration
      of speed and accuracy in solving real, non-linear problems.
  \end{itemize}}

  \item
     In Section 1.1.1, please include a more comprehensive literature review for
     the CS method, including fur ther references (some of them are listed below).
     In particular, specify what aspects of the CS method have been investigated in
     each reference. Then, you need to clearly mention your contribution within
     the CS method, in contrast to the other references (some comments in this
     regard appear in the manuscript in page 8).

{\color{red}
  \begin{itemize}
  \end{itemize}}

### 2014-02-21 response/candc.tex
first draft of lit review done

\subsection{Similarities with review work}

@@

\subsection{Differences with review work}

@@

\subsection{Differences with review work}

The prior work mentions employing CS within an iterative solver code for a sensitivity analysis, but
does not mention if CS is also used by the iterative solver itself.

@@

@@

\subsection{Similarities with review work}
\subsection{Differences with review work}
\subsection{Novelty of reviewed work}

@@

\subsection{Similarities with review work}
\subsection{Differences with review work}
\subsection{Novelty of reviewed work}

@@

\subsection{Similarities with review work}
\subsection{Differences with review work}
\subsection{Novelty of reviewed work}

@@

\subsection{Similarities with review work}
\subsection{Differences with review work}
\subsection{Novelty of reviewed work}

@@

\subsection{Similarities with review work}
\subsection{Differences with review work}
\subsection{Novelty of reviewed work}

@@

\subsection{Similarities with review work}
\subsection{Differences with review work}
\subsection{Novelty of reviewed work}

@@

\subsection{Similarities with review work}
\subsection{Differences with review work}
\subsection{Novelty of reviewed work}

@@

\subsection{Similarities with review work}
\subsection{Differences with review work}
\subsection{Novelty of reviewed work}

>>>>

\subsection{Similarities with reviewed work}

@@

\subsection{Differences with reviewed work}

@@

\subsection{Differences with reviewed work}

The prior work mentions employing CS within an iterative solver code within a sensitivity analysis, but
does not mention if CS is also used by the iterative solver itself.

@@

The reviewed work is about applying CS to solving Peridynamics problems using Newton's method, and is therefor about an
application of the derivatives produced by CS. The prior work is about the application of CS itself to produce derivatives
which themselves are the object of interest. The reviewed work is novel by comparison since it examines aspects of CS
different to those examined in the prior work.

@@

\subsection{Aspects of CS investigated}
Based on the accuracy of CS, the method is used to compute sensitivities in CFD
simulations. For the application of computing sensitivities, CS is compared to 
automatic differentiation.

\subsection{Similarities with reviewed work}
CS is used to compute derivatives and CS is compared to AD.

\subsection{Differences with reviewed work}
The prior work does not discus using the derivatives produced by CS to compute
the residual Jacobian, nor does it discuss the same for AD. The field is
fluid dynamics rather than solid mechanics, and the use of a prallel computer
is not discussed.

The reviewed work offers discussion on the use of CS and AD to compute
residual Jcobians and the effect of doing so on the performance of Newton's
method in Peridynamics simulations run on a parallel computer, where the prior
work discusses the derivitives produced by CS and AD themselves as the objects 
of interest.

@@

\subsection{Aspect of CS discussed}
The prior work investigates the use of complex step in computing Frechet derivatives 
of matix to matrix functions.

\subsection{Similarities with reviewed work}
To compute the residual Jacobian in the peridynamics simulation dicussed in the reviewed
work is essentially computing a Frechet derivative of a higher dimension function of higher
dimension variables.

\subsection{Differences with reviewed work}
Where the application of the CS derivatives in the prior work is limited to a particular 
class of abstract functions to determine the method's suitability for use in condition number
estimation, the reviewed work applies CS to solving a mechanics problem.

\subsection{Novelty of reviewed work}
Because the reviewed work is not about just computing Frechet derivatives with CS but using
them in a numerical method to solve a set of equations describing a physical system, the reviewed
work is largely different from the prior work.

@@

\subsection{Aspects of CS discussed}
The use of CS to compute sensitivities is disucssed in the contect of a solid mechanics
FEA analysis.

\subsection{Similarities with reviewed work}
CS is used to compute derivitives.

\subsection{Differences with reviewed work}
In the prior work the derivitives produced by CS themselves are the object of interest, where
the reviewed work uses CS in a numerical method for solving a non-linear system.

\subsection{Novelty of reviewed work}
The prior work and the reviewed work discuss different aspects of the CS method. The
reviewed work discusses using the CS in a numerical method to solve a non-linear system,
where the prior work discusses the derivatves produced by CS as an object of interest.

@@

\subsection{Aspect of CS discussed}
The prior work dicusses the background of the CS method and examines it as a subset
of Fourier Differentiation. CS and Fourier Differentiation are then applied to 
computing sensitivities within a solid mechanics FEA.

\subsection{Similarities with reviewed work}
CS is used to compute derivatives.

\subsection{Differences with reviewed work}
In the prior work, CS is discussed and related to a broader class of numerical methods. CS is then used
to compute sensitivities. In the reviewed work, complex step is used to compute residual Jacobians
which are used in Newton's method for solving non-linear systems.

\subsection{Novelty of reviewed work}
The reviewed work and prior work discuss different aspects of CS in that they examine different
applications of the method.

@@

\subsection{Aspects of CS discussed}
First and second order CS methods for computing derivatives. Choosing optimal
step size.

\subsection{Similarities with reviewed work}
Derivatives are computed with CS.

\subsection{Differences with reviewed work}
The prior work discusses computing first and second order accurate derivatives with CS and choosing optimal step size.
The reviewed work discussing using the derviatives computed with the CS method in a numerical method for solving 
a non-linear system.

\subsection{Novelty of reviewed work}
The reviewed work is offers discusion of the CS method as used in a numerical method for solving a non-linear system, where 
the prior work dicusses the derivatives produced by CS themselves as an object of interest.

@@

\subsection{Aspects of CS discussed}
Computing derivatives with CS is discussed. Combinations of real and imaginary step components
are studied to determine CS methods with extended accuracy order.

\subsection{Similarities with reviewed work}
Derivatives are computed with CS.

\subsection{Differences with reviewed work}
The prior work discusses using the CS method to compute derivatives and attempts to extend the
methods for that application. The reviewed work us the derivatives computed with CS in a numerical
method for solving a non-linear system.

\subsection{Novelty of reviewed work}
The prior work discusses the derviatives computed by the CS method as an object
of interest, while the reviewed work discusses using the derivatives computed
by the CS method in a numerical method for solving a non-linear system.
Because the the reviewed work and the prior work discuss different aspects of
CS and different applications, the reviewed work is novel.

@@

\subsection{Aspect of CS discussed}
The CS method is identified in an exact form.

\subsection{Similarities with reviewed work}
Derivatives are computed with the CS method.

\subsection{Differences with reviewed work}
The prior work develops the CS method, while the reviewed work
is about an application of the CS method.

\subsection{Novelty of reviewed work}
Because the reviewed work discusses an application the material presented in the
prior work not discussed in the prior work, it introduces novel material relative to the
prior work.

@@

\subsection{Aspects of CS discussed}
The series representation derived CS method is shown in its truncated form.

\subsection{Similarities with reviewed work}
Derivatives are computed with the CS method.

\subsection{Differences with reviewed work}
The prior work develops the CS method, while the reviewed work
is about an application of the CS method.

\subsection{Novelty of reviewed work}
Because the reviewed work discusses an application the material presented in the
prior work not discussed in the prior work, it introduces novel material relative to the
prior work.
